Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-03-06 scripts/02_differential_expression_analysis.Rmd
MAINT reactivating travis tests

```{r echo=FALSE, results="hide"}
# Hide those results
# Run the DE analysis on the rest of the influenza strain.
contrasts = c("M.0-K.0",
	      "M.3-K.3",
	      "M.6-K.6",
	      "M.9-K.9",
	      "M.12-K.12",
	      "M.18-K.18",
	      "M.24-K.24",
	      "M.30-K.30",
	      "M.36-K.36",
	      "M.48-K.48",
	      "M.60-K.60",
	      "M.72-K.72",
	      "M.120-K.120",
	      "M.168-K.168")
K_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-C.0",
	      "M.3-C.3",
	      "M.6-C.6",
	      "M.9-C.9",
	      "M.12-C.12",
	      "M.18-C.18",
	      "M.24-C.24",
	      "M.30-C.30",
	      "M.36-K.36",
	      "M.48-C.48",
	      "M.60-C.60",
	      "M.72-C.72",
	      "M.120-C.120",
	      "M.168-C.168")
C_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-VH.0",
	      "M.3-VH.3",
	      "M.6-VH.6",
	      "M.9-VH.9",
	      "M.12-VH.12",
	      "M.18-VH.18",
	      "M.24-VH.24",
	      "M.30-VH.30",
	      "M.36-VH.36",
	      "M.48-VH.48",
	      "M.60-VH.60",
	      "M.72-VH.72",
	      "M.120-VH.120",
	      "M.168-VH.168")
VH_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
```

@@

```{r}
print(colSums(pvalues[, grepl("-qval", colnames(pvalues))] < 0.05))
```

>>>>

```{r echo=FALSE, results="hide"}
# Hide those results
# Run the DE analysis on the rest of the influenza strain.
contrasts = c("M.0-K.0",
	      "M.3-K.3",
	      "M.6-K.6",
	      "M.9-K.9",
	      "M.12-K.12",
	      "M.18-K.18",
	      "M.24-K.24",
	      "M.30-K.30",
	      "M.36-K.36",
	      "M.48-K.48",
	      "M.60-K.60",
	      "M.72-K.72",
	      "M.120-K.120",
	      "M.168-K.168")
K_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-C.0",
	      "M.3-C.3",
	      "M.6-C.6",
	      "M.9-C.9",
	      "M.12-C.12",
	      "M.18-C.18",
	      "M.24-C.24",
	      "M.30-C.30",
	      "M.36-K.36",
	      "M.48-C.48",
	      "M.60-C.60",
	      "M.72-C.72",
	      "M.120-C.120",
	      "M.168-C.168")
C_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-VH.0",
	      "M.3-VH.3",
	      "M.6-VH.6",
	      "M.9-VH.9",
	      "M.12-VH.12",
	      "M.18-VH.18",
	      "M.24-VH.24",
	      "M.30-VH.30",
	      "M.36-VH.36",
	      "M.48-VH.48",
	      "M.60-VH.60",
	      "M.72-VH.72",
	      "M.120-VH.120",
	      "M.168-VH.168")
VH_weekly_de_analysis =  moanin::weekly_differential_expression_analysis(
     data, meta, contrasts,
     use_voom_weights=FALSE)

@@

```{r echo=FALSE, fig.width=6}
num_de = colSums(qvalues < 0.05)
names(num_de) = c(
    "Kawasaki", "California", "Vietnam low-dose", "Vietname high-dose")
barplot(num_de, col="black", ylab="Number of DE genes")

### 2019-03-06 scripts/04_downstream_analysis.Rmd
MAINT reactivating travis tests

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
library(KEGGprofile)
```

@@

```{r echo=FALSE}
library(kableExtra)
library(viridis)

@@

cluster = c(3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

@@

```{r echo=FALSE}
library(kableExtra)

all_go_terms = all_go_terms[
    order(all_go_terms[, "Cluster"],
	  all_go_terms[, "resultFisher_padj"]), ]

>>>>

```{r echo=FALSE, results="hide", message=FALSE}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(KEGGprofile)
library(kableExtra)
library(viridis)

library(moanin)
```

@@

```{r echo=FALSE}

@@

cluster = c(1, 2, 3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

@@

```{r echo=FALSE}

all_go_terms = all_go_terms[
    order(all_go_terms[, "Cluster"],
	  all_go_terms[, "Ontology"],
	  all_go_terms[, "resultFisher_padj"]), ]
